Generalized Plackett-Luce Likelihoods

### 2022-08-04 inst/jss_hyper3.Rnw
cite Mann and Whitney 1947

The ideas presented above can easily be extended to arbitrarily large
numbers of competitors.  Given an order statistic of the type
considered above, the Mann-Whitney-Wilcoxon test assesses a null of
identity of underlying distributions.  Consider the fly spray dataset
presented by \cite{wilcoxon1945}:

>>>>

The ideas presented above can easily be extended to arbitrarily large
numbers of competitors.  Given an order statistic of the type
considered above, the Mann-Whitney-Wilcoxon
test~\citep{mann1947,wilcoxon1945} assesses a null of identity of
underlying distributions.  Consider the fly spray dataset presented by
\citeauthor{wilcoxon1945}:
